Review: Redefining Domestication: Adaptive Introgression during Crop Expansion

### 2017-06-09 paper.tex
edits through introgression methods

Adaptive introgression has three components: hybridization between two genomes, backcrossing to one of the parents, and selection on different recombinant genotypes with progressively diminished linkage drag \cite{barton2001role, Feuillet200824}.
In domesticated species, adaptive introgression would consist of crop/wild hybrids backcrossing to a crop, retention and increase in frequency of adaptive wild haplotypes in the crop, and removal of undesirable wild background.
Literature on crop-wild gene flow has focused on the risk of introgression of transgenes from domesticated crops into wild relatives (for a review, \cite{stewart2003transgene}) and on modern plant breeding efforts to introgress desired traits from wild relatives (for a review, \cite{zamir2001improving, tanksley1997seed, hajjar2007use}).
The history of natural introgression of wild alleles into domesticated crops over evolutionary timescales has received considerably less attention.
Recent tools and methods have been employed to detect genome-wide patterns of introgression, granting new insights into the prevalence of adaptive introgression in crop histories.
Emerging results suggest a need for reevaluation of the existing domestication paradigm.

@@

First, introgressed segments are expected to show low differentiation from their source population.
The $F_{st}$ and $d_{XY}$ statistics and their derivates such as $G_{min}$ \cite{geneva2015} and $RND_{min}$\cite{rosenzweig2016} gauge differentiation. 
The former two are insensitive to rare migrants and therefore lack power to detect recent introgression, while the latter two overcome this limitation.
Additionally, $RND_{min}$ accounts for variable mutation rate, which is detected based on branch length to an outgroup.

@@

These statistics have recently been further developed by adding differentiation between both non-admixed ($A$) and admixed populations ($B$) and a source population ($C$) \cite{racimo2016}. 
For example, the $U_{A,B,C(w,x,y)}$ statistic summarizes number of sites, where an allele at frequency $y$ in the source population ($C$) has a frequency higher than $x$ in the admixed population ($B$) and lower than $w$ in the non-admixed population ($C$).
A similar statistic, $Q95_{A,B,C(w,y)}$, sets a hard cutoff at the $95^th$ percentile of allele frequencies in the admixed population (B) \cite{racimo2016}.
\mbh{not quite sure I follow here, needs to be made more clear} 
These statistics were further developed to allow specification two source populations (see details in \cite{racimo2016}).

Second, local ancestry reconvolution (also known as chromosome painting) can identify the genomic regions that come from different source populations \cite{schraiber2015}. 
Such methods usually take phased haplotypes as input, but MULTIMIX \cite{churchhouse2013} can take both phased and unphased haplotypes as input, unveiling the genomic ancestry from multiple source populations.

Third, ABBA-BABA statistics (also known as D-statistics) and their derivatives are widely applied to the search for signs of introgression in genomic patterns of shared derived variants between populations or species. 
Based on D-statistics, $\hat{f_{d}}$ \cite{Martin2015} and five-taxon D statistics \cite{pease2015} were developed to localize genomic regions under introgression. 
The former took allele frequencies from each population/species, and the latter detected introgression from the localized phylogenetic pattern.
Their strength in identifying specific regions enables one to explore the relationships between introgression and recombination rate/gene density/distribution of deleterious alleles and to better understand the genomic regions penetrable to foreign gene flow.

Fourth, structure-related approaches are based on the popular software STRUCTURE \cite{pritchard2000}, which provides an estimate of the fraction of each individual's genome coming from each population. 
Many approaches in this respect have been developed.
Two of these, fineSTRUCTURE \cite{Lawson2012} and GLOBETROTTER \cite{hellenthal2014}, were selected as representations.
Different from STRUCTURE, fineSTRUCTURE not only identifies the number of populations, but also estimates the probability that genomic regions belong to one or the other populations. 
GLOBETROTTER is a development of fineSTRUCTURE that allows for tracing back to an unsampled source population and dating admixture events.

Application of these approaches across a number of plant and animal species suggests introgression can play an adaptive role. For example, introgression from ancient hominins (\emph{e.g.}, Neanderthals and Denisovans) to humans has been detected at loci controlling skin pigmentation, defense against pathogens, and toleration of high altitude (reviewed in \cite{Racimo2015}), introgression has conferred M\"{u}llerian mimicry across butterfly species (\cite{Heliconius2012}; introgression has spread insecticide resistance across mosquito species \cite{Norris2015}, and introgression across \emph{Mimulus} (\emph{i.e.}, monkeyflower) species has resulted in adaptation to pollinator preference and contributed to speciation \cite{Stankowski2015}.

>>>>

Adaptive introgression has three components: hybridization between two genomes, backcrossing to one of the parents, and selection on different recombinant genotypes with progressively diminished linkage drag \cite{barton2001role, Feuillet200824}.
In domesticated species, adaptive introgression would consist of crop/wild hybrids backcrossing to a crop, retention and increase in frequency of adaptive wild haplotypes in the crop, and removal of undesirable wild background.
To date, literature on crop-wild gene flow has focused on the risk of introgression of transgenes from domesticated crops into wild relatives (for a review, \cite{stewart2003transgene}) and on modern plant breeding efforts to introgress desired traits from wild relatives (for a review, \cite{zamir2001improving, tanksley1997seed, hajjar2007use}). \mbh{cite one paper here...the best, most recent and comprehensive review}
The history of natural introgression of wild alleles into domesticated crops over evolutionary timescales has received considerably less attention.
However, recent tools and methods have been employed to detect genome-wide patterns of introgression, granting new insights into the prevalence of adaptive introgression in crop histories.
Emerging results suggest a need for reevaluation of the existing domestication paradigm.

@@

First, introgressed segments are expected to show low differentiation from their source population.
The $F_{st}$ and $d_{XY}$ statistics and their derivates including $G_{min}$ \cite{geneva2015} and $RND_{min}$\cite{rosenzweig2016} gauge differentiation. 
The former two statistics are insensitive to rare migrants and therefore lack power to detect recent introgression, while the latter two overcome this limitation.
Additionally, $RND_{min}$ accounts for variable mutation rate, which is detected based on branch length to an outgroup.

@@

These statistics have recently been further developed by adding differentiation between both non-admixed ($A$) and admixed populations ($B$) and a source population ($C$) \cite{racimo2016}. 
For example, the $U_{A,B,C(w,x,y)}$ statistic summarizes number of sites, where an allele at frequency $y$ in the source population ($C$) has a frequency higher than $x$ in the admixed population ($B$) and lower than $w$ in the non-admixed population ($C$).
A similar statistic, $Q95_{A,B,C(w,y)}$, sets a hard cutoff at the $95^{th}$ percentile of allele frequencies in the admixed population (B) \cite{racimo2016}.
\mbh{Did I get this right, Li?} 
Further modifications have allowed specification of two source populations (see details in \cite{racimo2016}).

Second, local ancestry deconvolution (also known as chromosome painting) assigns genomic regions to various source populations \cite{schraiber2015}. \mbh{How?  How do these methods work?  I know at least some are based on Hidden Markov Models...need a sentence or two on the nuts and bolts}
Such methods typically require phased haplotypes as input (but see \cite{churchhouse2013}).

Third, the ABBA-BABA statistic (also known as the D-statistic) and its derivatives are widely applied to introgression detection and make inferences based on genomic patterns of shared derived variants between populations or species in a phylogenetic context. \mbh{need sentence here explaining what D-statistic does} 
Elaborations of the D-statistic include $\hat{f_{d}}$ \cite{Martin2015} and the five-taxon D-statistic \cite{pease2015}. 
The former is quite similar to the D-statistic but uses allele frequencies from each population/species, and the latter detects introgression based on the localized phylogenetic pattern. \mbh{need to clarify here how this is different than $\hat{f_{d}}$}
%Their strength in identifying specific regions enables one to explore the relationships between introgression and recombination rate/gene density/distribution of deleterious alleles and to better understand the genomic regions penetrable to foreign gene flow.

Fourth, approaches that assign genome-wide genetic ancestry are based on the popular software STRUCTURE \cite{pritchard2000}. 
For example, fineSTRUCTURE \cite{Lawson2012} calculates the probability that genomic regions belong to genetic groups by \mbh{need details on method here}. 
GLOBETROTTER \cite{hellenthal2014} is a further development of fineSTRUCTURE that allows for identification of an unsampled source population and for dating of admixture events.

Application of these approaches across a number of plant and animal species suggests introgression can play an adaptive role. For example, introgression from ancient hominins (\emph{e.g.}, Neanderthals and Denisovans) to humans has been detected at loci controlling skin pigmentation, defense against pathogens, and toleration of high altitude (reviewed in \cite{Racimo2015}), introgression has conferred M\"{u}llerian mimicry \mbh{I would explain a bit more here...wing coloration loci, protects against predation...} across butterfly species \cite{Heliconius2012} introgression has spread insecticide resistance across mosquito species \cite{Norris2015}, and introgression across \emph{Mimulus} (\emph{i.e.}, monkeyflower) species has resulted in adaptation to pollinator preference and contributed to speciation \cite{Stankowski2015}.
